Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-14 Manuscript/Tmatrix.tex
modifs pina

In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start \titou{from the equation for the BSE right-hand side electron-hole amplitude?!}

@@

\begin{equation}
	\label{eq:egval}
	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} \titou{-} \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
\end{equation}
%with $$\langle ab|ij\rangle=\int d\bx_1d\bx_2 \SO{a}(\bx_1) \SO{b}(\bx_2)v(\bx_1,\bx_2) \SO{i}(\bx_1) \SO{j}(\bx_2),$$ 
where the spectral representation of the dynamical $T$-matrix is
\begin{equation}
	\widetilde{T}_{ib,aj}(\omega_S)
	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}\right]. 
 \label{eq:H2preso_eigen_2_T}
\end{equation}
Equation \eqref{eq:egval} represents a non-linear eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as
\begin{equation}
\label{eq:H2preso_eigen}
	\titou{\sum_{jb}} A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
\end{equation}
with
\begin{equation}
	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} \titou{-} \widetilde{T}_{ib,aj}(\omega_S).
\end{equation}
%Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
To calculate the correlation contribution, one must employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.

>>>>

In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE  amplitude

@@

\begin{equation}
	\label{eq:egval}
	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} - \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
\end{equation}
%with $$\langle ab|ij\rangle=\int d\bx_1d\bx_2 \SO{a}(\bx_1) \SO{b}(\bx_2)v(\bx_1,\bx_2) \SO{i}(\bx_1) \SO{j}(\bx_2),$$ 
where the spectral representation of the dynamical $T$-matrix is
\begin{equation}
	\widetilde{T}_{ib,aj}(\omega_S)
	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}\right]. 
 \label{eq:H2preso_eigen_2_T}
\end{equation}
Equation \eqref{eq:egval} represents a non-linear eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as
\begin{equation}
\label{eq:H2preso_eigen}
	\sum_{jb} A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
\end{equation}
with
\begin{equation}
	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega_S).
\end{equation}
%Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
To calculate the correlation contribution, one must employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
